%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------    

\cventry
{Accident Sketch} % Job title
{Dofleini} % Organization
{La Havana, Cuba} % Location
{Nov. 2016 - Dic. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implement a solution using JavaScript to draw sketches of accidents and execute little kinetics simulations}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Police Management System} % Job title
{Dofleini} % Organization
{La Havana, Cuba} % Location
{Aug. 2015 - Sep. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {It is a custom development for police stations in Tarragona Spain. Specially design to cover the main needs of police daily.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{3D Virtual Environment for Visualization of Simulations Logistics Operations a Robotic System Container Management} % Job title
{In collaboration with the International Center of Numerical Methods applied to Engineering (CIMNE) Polytechnic University of Cataluña, Spain.} % Organization
{La Havana, Cuba} % Location
{2015 - 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Design and develop a desktop application using C# and Unity for the visualization in three dimensions of Simulations Logistics Operations a Robotic System Container Management.}
}

%------------------------------------------------

\cventry
{Multilayered geographic information Representation, based on Digital Elevation Models for the development and analysis of 3D simulations.} % Job title
{In collaboration with the International Center of Numerical Methods applied to Engineering (CIMNE) Polytechnic University of Cataluña, Spain} % Organization
{La Havana, Cuba} % Location
{Sep. 2014 - Jul. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Development of improvements to the data structures used in the simulations' render process resulting in an performance increase from 50 layers per simulation to 5000 layers per simulation.}
%\item {}
\end{cvitems}
}

%------------------------------------------------
\cventry
{Web component for 3D visualization of Digital Elevation Models} % Job title
{Centre of Internet Studies (University of Informatics Science)} % Organization
{La Havana, Cuba} % Location
{2013 - 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {The project focuses on using efficiently computing resources available on workstations to achieve the creation of a base layer for the representation of 3D terrain on the Web, this approach had an added value by to reduce the workload on the server and this can serve more concurrent requests.}
%\item {}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Integrated Development Environment for Assemblers Languages} % Job title
{University of Informatics Science} % Organization
{La Havana, Cuba} % Location
{Sep. 2011 - Jul. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Multiplatform IDE for Assemblers Languages using FASM compiler.}
%\item {}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}

