%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Positions}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------    

\cventry
{Front-End Web Developer} % Job title
{Dofleini} % Organization
{La Havana, Cuba} % Location
{Nov. 2016 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Front end development REST Web Apps}
\item {Javascript/HTML/CSS/LESS/SASS}
\end{cvitems}
}
%------------------------------------------------

\cventry
{Front-End Web Developer} % Job title
{OpenJAF} % Organization
{La Havana, Cuba} % Location
{Feb. 2016 - Oct. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed front-end user interface experience on websites using AngularJS and EmberJS techniques}
\end{cvitems}
}
%------------------------------------------------

\cventry
{Junior Researcher} % Job title
{Centre of Internet Studies (University of Informatics Science)} % Organization
{La Havana, Cuba} % Location
{2013 - 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Design, develop and document a javascript library to visualize and process 3D simulation on web browsers using Web Workers and WebGL, it is focus on increase the level of information processing in the client and reduce the server workload, resulting in an increase in the server's rate response}
\item {Design and develop a desktop application using C# and OpenGL for the visualization in three dimensions of big simulations over terrains.}
\item {Development of improvements to the data structures used in the simulations' render process resulting in an performance increase from 50 layers per simulation to 5000 layers per simulation.}
\item {Design and develop a desktop application using C# and Unity for the visualization in three dimensions of Simulations Logistics Operations a Robotic System Container Management}
\end{cvitems} 
}


%------------------------------------------------

\cventry
{Software Developer} % Job title
{Cuba PostgreSQL Group (University of Informatics Science)} % Organization
{La Havana, Cuba} % Location
{Sep. 2013 - Jul. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Create and customize multiplatform tools using Java for assist applications which use PostgreSQL like database system.}
%\item {}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}

